---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 6,
  fig.height = 6
)
```

# sketchpad

<!-- badges: start -->
[![R-CMD-check](https://github.com/djnavarro/sketchpad/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/djnavarro/sketchpad/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/djnavarro/sketchpad/graph/badge.svg)](https://app.codecov.io/gh/djnavarro/sketchpad)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

sketchpad is a lightweight, [p5.js](https://p5js.org/)-inspired drawing
system for generative art, built on [S7](https://rconsortium.github.io/S7/)
classes and `grid` graphics. It provides a small set of `drawable` shapes
(`shape_circle()`, `shape_blob()`, `shape_ribbon()`, `shape_twist()`) that
can be composed into a `sketch()` and rendered with `draw()`.

## Installation

You can install the development version of sketchpad from
[GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("djnavarro/sketchpad")
```

## A ring of blobs

A `shape_blob()` is a circle whose radius is perturbed by simplex noise. Here six
blobs are arranged around a ring, one per colour:

```{r ring-of-blobs}
library(sketchpad)

values <- tibble::tibble(
  x = cos(seq(0, pi * 5 / 3, length.out = 6)),
  y = sin(seq(0, pi * 5 / 3, length.out = 6)),
  n = 500L,
  fill = c("#e50000", "#ff8d00", "#ffee00", "#028121", "#004cff", "#770088"),
  color = fill
)
blobs <- purrr::pmap(values, shape_blob)
blobs |> sketch() |> draw()
```

## Scattered blobs

Randomising the position, radius, and noise range of many blobs gives a
more organic composition:

```{r scattered-blobs}
set.seed(3)
palette <- c("#e50000", "#ff8d00", "#ffee00", "#028121", "#004cff", "#770088")
n_blobs <- 200L
values <- tibble::tibble(
  x = rnorm(n_blobs, sd = 1.5),
  y = rnorm(n_blobs, sd = 1.5),
  n = 500L,
  fill = sample(palette, n_blobs, replace = TRUE),
  radius = runif(n_blobs),
  range = runif(n_blobs, min = 0, max = .5),
  color = fill
)
blobs <- purrr::pmap(values, shape_blob)
blobs |> sketch() |> draw(xlim = c(-2, 2), ylim = c(-2, 2))
```

## Ribbons

A `shape_ribbon()` is a tapered, noise-displaced band drawn between two points:

```{r ribbons}
set.seed(3)
palette <- c("#e50000", "#ff8d00", "#ffee00", "#028121", "#004cff", "#770088")
n_ribbons <- 200L
values <- tibble::tibble(
  x = rnorm(n_ribbons, sd = 1.5),
  y = rnorm(n_ribbons, sd = 1.5),
  xend = x + 1,
  yend = y,
  width = 1,
  n = 500L,
  fill = sample(palette, n_ribbons, replace = TRUE),
  color = fill
)
ribbons <- purrr::pmap(values, shape_ribbon)
ribbons |> sketch() |> draw(xlim = c(-2, 2), ylim = c(-2, 2))
```

## Twists

A `shape_twist()` is like a ribbon, but follows a Brownian bridge instead of a
straight line, giving it a wandering, twisted appearance:

```{r twists}
set.seed(1)
palette <- c("#de9151", "#f34213", "#2e2e3a", "#bc5d2e", "#bbb8b2")
n_twists <- 400L
values <- tibble::tibble(
  x = rnorm(n_twists, sd = 2),
  y = rnorm(n_twists, sd = 2),
  xend = x + 1,
  yend = y + rnorm(n_twists, sd = 1),
  width = runif(n_twists, min = .1, max = .3),
  smooth = 6L,
  n = 100L,
  fill = sample(palette, n_twists, replace = TRUE),
  color = fill
)
twists <- purrr::pmap(values, shape_twist)
twists |> sketch() |> draw(xlim = c(-2, 2), ylim = c(-2, 2))
```


